Outdated and License-Violating Code on Stack Overflow

### 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
Modified the paper according to Rocco's comments.

Given that a clone pair \textit{CP} is formed by two clone fragments
\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} = (\textit{CF$_1$},
\textit{CF$_2$}), we can define the \textit{overlap}\footnote{The overlap value can be considered as Jaccard similarity.} and
\textit{contained} value of two clone pairs as
%\squeezeup
\begin{displaymath}
  overlap(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
\end{displaymath}
% \squeezeup
\begin{displaymath}
  contained(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
\end{displaymath}

\noindent%
The \textit{good-value}  and the \textit{ok-value}  of two clone pairs are defined as
%\squeezeup
\begin{align*}
	good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2))
\end{align*}
\begin{align*}
	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1),~~ \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),~
	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2),~~ \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2)))
\end{align*}

@@

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection (67,570
for $S_D$ and 632,855 pairs for $N_D$). We applied two filters: clone
size and similarity threshold. %, and good/ok pairs. 
For the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
The second filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. 
%The last filter, \emph{good/ok pairs}, removes the clone pairs that already exist in the agreed clone sets.
%As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and gook/ok pairs.

>>>>

We define the \textit{overlap}\footnote{The overlap value can be considered as Jaccard similarity.} and
\textit{contained} value of two clone fragments (\textit{CF}) as
%\squeezeup
\begin{displaymath}
  overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
\end{displaymath}
% \squeezeup
\begin{displaymath}
  contained(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
\end{displaymath}

\noindent%
Given that a clone pair \textit{CP} is formed by two clone fragments
\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} = (\textit{CF$_1$},
\textit{CF$_2$}), the \textit{good-value}  and the \textit{ok-value}  of two clone pairs are defined as
%\squeezeup
\begin{align*}
	good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2))
\end{align*}
\begin{align*}
	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1),~~ \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),~
	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2),~~ \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2)))
\end{align*}

@@

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection.
%(67,570 for $S_D$ and 632,855 pairs for $N_D$). 
We applied two filters: clone
size and similarity threshold. %, and good/ok pairs. 
For the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
The second filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. 
%The last filter, \emph{good/ok pairs}, removes the clone pairs that already exist in the agreed clone sets.
%As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and gook/ok pairs.
